---
title: "LaTeX Raw Page 01"
author: "Shawn Garbett"
date: "July 13, 2018"
output:
  pdf_document:
    keep_tex: yes
header-includes:
- \usepackage[LGR,T1,T4]{fontenc}
- \usepackage[utf8]{inputenc}
- \usepackage{textgreek}
- \usepackage{amsmath,mathtools}
- \usepackage{textcomp}
- \usepackage{tipx}
- \usepackage{ipa}
- \usepackage{combelow}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tangram)
library(stringi)
```

```{r}
p <- function(...) { cat(paste0(...)); invisible(NULL) }
l <- function(...) { cat(tangram:::latexify(...)); invisible(NULL) }
```

## R Markdown
```{r, results='asis'}
p("\\textbf{This is a test of LaTeX}")
```

Working on u0100

```{r, results="asis"}
l("\u0100")
```

Working on u0101

```{r, results="asis"}
l("\u0101")
```


Working on u0102

```{r, results="asis"}
l("\u0102")
```

Working on u0103

```{r, results="asis"}
l("\u0103")
```

Working on u0104

```{r, results="asis"}
l("\u0104")
```

Working on u0105

```{r, results="asis"}
l("\u0105")
```

Working on u0106

```{r, results="asis"}
l("\u0106")
```

Working on u0107

```{r, results="asis"}
l("\u0107")
```

Working on u0108

```{r, results="asis"}
l("\u0108")
```

Working on u0109

```{r, results="asis"}
l("\u0109")
```

Working on u010A

```{r, results="asis"}
l("\u010A")
```

Working on u010B

```{r, results="asis"}
l("\u010B")
```

Working on u010C

```{r, results="asis"}
l("\u010C")
```

Working on u010D

```{r, results="asis"}
l("\u010D")
```

Working on u010E

```{r, results="asis"}
l("\u010E")
```

Working on u010F

```{r, results="asis"}
l("\u010F")
```


Working on u0110

```{r, results="asis"}
l("\u0110")
```

Working on u0111

```{r, results="asis"}
l("\u0111")
```

Working on u0112

```{r, results="asis"}
l("\u0112")
```

Working on u0113

```{r, results="asis"}
l("\u0113")
```

Working on u0114

```{r, results="asis"}
l("\u0114")
```

Working on u0115

```{r, results="asis"}
l("\u0115")
```

Working on u0116

```{r, results="asis"}
l("\u0116")
```

Working on u0117

```{r, results="asis"}
l("\u0117")
```

Working on u0118

```{r, results="asis"}
l("\u0118")
```

Working on u0119

```{r, results="asis"}
l("\u0119")
```

Working on u011A

```{r, results="asis"}
l("\u011A")
```

Working on u011B

```{r, results="asis"}
l("\u011B")
```

Working on u011C

```{r, results="asis"}
l("\u011C")
```

Working on u011D

```{r, results="asis"}
l("\u011D")
```

Working on u011E

```{r, results="asis"}
l("\u011E")
```

Working on u011F

```{r, results="asis"}
l("\u011F")
```


Working on u0120

```{r, results="asis"}
l("\u0120")
```

Working on u0121

```{r, results="asis"}
l("\u0121")
```

Working on u0122

```{r, results="asis"}
l("\u0122")
```

Working on u0123

```{r, results="asis"}
l("\u0123")
```

Working on u0124

```{r, results="asis"}
l("\u0124")
```

Working on u0125

```{r, results="asis"}
l("\u0125")
```

Working on u0126

```{r, results="asis"}
l("\u0126")
```

Working on u0127

```{r, results="asis"}
l("\u0127")
```

Working on u0128

```{r, results="asis"}
l("\u0128")
```

Working on u0129

```{r, results="asis"}
l("\u0129")
```

Working on u012A

```{r, results="asis"}
l("\u012A")
```

Working on u012B

```{r, results="asis"}
l("\u012B")
```

Working on u012C

```{r, results="asis"}
l("\u012C")
```

Working on u012D

```{r, results="asis"}
l("\u012D")
```

Working on u012E

```{r, results="asis"}
l("\u012E")
```

Working on u012F

```{r, results="asis"}
l("\u012F")
```


Working on u0130

```{r, results="asis"}
l("\u0130")
```

Working on u0131

```{r, results="asis"}
l("\u0131")
```

Working on u0132

```{r, results="asis"}
l("\u0132")
```

Working on u0133

```{r, results="asis"}
l("\u0133")
```

Working on u0134

```{r, results="asis"}
l("\u0134")
```

Working on u0135

```{r, results="asis"}
l("\u0135")
```

Working on u0136

```{r, results="asis"}
l("\u0136")
```

Working on u0137

```{r, results="asis"}
l("\u0137")
```

Working on u0138

```{r, results="asis"}
l("\u0138")
```


Working on u0139

```{r, results="asis"}
l("\u0139")
```

Working on u013A

```{r, results="asis"}
l("\u013A")
```

Working on u013B

```{r, results="asis"}
l("\u013B")
```

Working on u013C

```{r, results="asis"}
l("\u013C")
```

Working on u013D

```{r, results="asis"}
l("\u013D")
```

Working on u013E

```{r, results="asis"}
l("\u013E")
```

Working on u013F

```{r, results="asis"}
l("\u013F")
```

Working on u0140

```{r, results="asis"}
l("\u0140")
```

Working on u0141

```{r, results="asis"}
l("\u0141")
```

Working on u0142

```{r, results="asis"}
l("\u0142")
```

Working on u0143

```{r, results="asis"}
l("\u0143")
```

Working on u0144

```{r, results="asis"}
l("\u0144")
```

Working on u0145

```{r, results="asis"}
l("\u0145")
```

Working on u0146

```{r, results="asis"}
l("\u0146")
```

Working on u0147

```{r, results="asis"}
l("\u0147")
```

Working on u0148

```{r, results="asis"}
l("\u0148")
```

Working on u0149

```{r, results="asis"}
l("\u0149")
```

Working on u014A

```{r, results="asis"}
l("\u014A")
```

Working on u014B

```{r, results="asis"}
l("\u014B")
```

Working on u014C

```{r, results="asis"}
l("\u014C")
```

Working on u014D

```{r, results="asis"}
l("\u014D")
```

Working on u014E

```{r, results="asis"}
l("\u014E")
```

Working on u014F

```{r, results="asis"}
l("\u014F")
```


Working on u0150

```{r, results="asis"}
l("\u0150")
```

Working on u0151

```{r, results="asis"}
l("\u0151")
```

Working on u0152

```{r, results="asis"}
l("\u0152")
```

Working on u0153

```{r, results="asis"}
l("\u0153")
```

Working on u0154

```{r, results="asis"}
l("\u0154")
```

Working on u0155

```{r, results="asis"}
l("\u0155")
```

Working on u0156

```{r, results="asis"}
l("\u0156")
```

Working on u0157

```{r, results="asis"}
l("\u0157")
```

Working on u0158

```{r, results="asis"}
l("\u0158")
```

Working on u0159

```{r, results="asis"}
l("\u0159")
```

Working on u015A

```{r, results="asis"}
l("\u015A")
```

Working on u015B

```{r, results="asis"}
l("\u015B")
```

Working on u015C

```{r, results="asis"}
l("\u015C")
```

Working on u015D

```{r, results="asis"}
l("\u015D")
```

Working on u015E

```{r, results="asis"}
l("\u015E")
```

Working on u015F

```{r, results="asis"}
l("\u015F")
```


Working on u0160

```{r, results="asis"}
l("\u0160")
```

Working on u0161

```{r, results="asis"}
l("\u0161")
```

Working on u0162

```{r, results="asis"}
l("\u0162")
```

Working on u0163

```{r, results="asis"}
l("\u0163")
```

Working on u0164

```{r, results="asis"}
l("\u0164")
```

Working on u0165

```{r, results="asis"}
l("\u0165")
```

Working on u0166

```{r, results="asis"}
l("\u0166")
```

Working on u0167


```{r, results="asis"}
l("\u0167")
```

Working on u0168

```{r, results="asis"}
l("\u0168")
```

Working on u0169

```{r, results="asis"}
l("\u0169")
```

Working on u016A

```{r, results="asis"}
l("\u016A")
```

Working on u016B

```{r, results="asis"}
l("\u016B")
```

Working on u016C

```{r, results="asis"}
l("\u016C")
```

Working on u016D

```{r, results="asis"}
l("\u016D")
```

Working on u016E

```{r, results="asis"}
l("\u016E")
```

Working on u016F

```{r, results="asis"}
l("\u016F")
```

Working on u0170

```{r, results="asis"}
l("\u0170")
```

Working on u0171

```{r, results="asis"}
l("\u0171")
```

Working on u0172

```{r, results="asis"}
l("\u0172")
```

Working on u0173

```{r, results="asis"}
l("\u0173")
```

Working on u0174

```{r, results="asis"}
l("\u0174")
```

Working on u0175

```{r, results="asis"}
l("\u0175")
```

Working on u0176

```{r, results="asis"}
l("\u0176")
```

Working on u0177

```{r, results="asis"}
l("\u0177")
```

Working on u0178

```{r, results="asis"}
l("\u0178")
```

Working on u0179

```{r, results="asis"}
l("\u0179")
```

Working on u017A

```{r, results="asis"}
l("\u017A")
```

Working on u017B

```{r, results="asis"}
l("\u017B")
```

Working on u017C

```{r, results="asis"}
l("\u017C")
```

Working on u017D

```{r, results="asis"}
l("\u017D")
```

Working on u017E

```{r, results="asis"}
l("\u017E")
```

Working on u017F

```{r, results="asis"}
l("\u017F")
```


Working on u0180

```{r, results='asis'}
l('\u0180')
```

Working on u0181

```{r, results='asis'}
l('\u0181')
```

Working on u0182

```{r, results='asis'}
l('\u0182')
```

Working on u0183

```{r, results='asis'}
l('\u0183')
```

Working on u0184

```{r, results='asis'}
l('\u0184')
```

Working on u0185

```{r, results='asis'}
l('\u0185')
```

Working on u0186

```{r, results='asis'}
l('\u0186')
```

Working on u0187

```{r, results='asis'}
l('\u0187')
```

Working on u0188

```{r, results='asis'}
l('\u0188')
```

Working on u0189

```{r, results='asis'}
l('\u0189')
```

Working on u018A

```{r, results='asis'}
l('\u018A')
```

Working on u018B

```{r, results='asis'}
l('\u018B')
```

Working on u018C

```{r, results='asis'}
l('\u018C')
```

Working on u018D

```{r, results='asis'}
l('\u018D')
```

Working on u018E

```{r, results='asis'}
l('\u018E')
```

Working on u018F

```{r, results='asis'}
l('\u018F')
```

Working on u0190

```{r, results='asis'}
l('\u0190')
```

Working on u0191

```{r, results='asis'}
l('\u0191')
```

Working on u0192

```{r, results='asis'}
l('\u0192')
```

Working on u0193

```{r, results='asis'}
l('\u0193')
```

Working on u0194

```{r, results='asis'}
l('\u0194')
```

Working on u0195

```{r, results="asis"}
l("\u0195")
```

Working on u0196

```{r, results='asis'}
l('\u0196')
```

Working on u0197

```{r, results='asis'}
l('\u0197')
```

Working on u0198

```{r, results='asis'}
l('\u0198')
```

Working on u0199

```{r, results='asis'}
l('\u0199')
```


Working on u019E

```{r, results="asis"}
l("\u019E")
```

Working on u019F

```{r, results="asis"}
l("\u019F")
```

Working on u01A0

```{r, results="asis"}
l("\u01A0")
```

Working on u01A1

```{r, results="asis"}
l("\u01A1")
```

Working on u01A2

```{r, results="asis"}
l("\u01A2")
```

Working on u01A3

```{r, results="asis"}
l("\u01A3")
```

Working on u01A4

```{r, results="asis"}
l("\u01A4")
```

Working on u01A5

```{r, results="asis"}
l("\u01A5")
```

Working on u01A6

*UNSUPPORTED*

Working on u01A7

```{r, results="asis"}
l("\u01A7")
```

Working on u01A8

```{r, results="asis"}
l("\u01A8")
```

Working on u01A9

```{r, results="asis"}
l("\u01A9")
```

Working on u01AA

```{r, results="asis"}
l("\u01AA")
```

Working on u01AB

```{r, results="asis"}
l("\u01AB")
```

Working on u01AC

```{r, results="asis"}
l("\u01AC")
```

Working on u01AD

```{r, results="asis"}
l("\u01AD")
```

Working on u01AE

```{r, results="asis"}
l("\u01AE")
```

Working on u01AF

```{r, results="asis"}
l("\u01AF")
```

Working on u01B0

```{r, results="asis"}
l("\u01B0")
```

Working on u01B1

```{r, results="asis"}
l("\u01B1")
```

Working on u01B2

```{r, results="asis"}
l("\u01B2")
```

Working on u01B3

```{r, results="asis"}
l("\u01B3")
```

Working on u01B4

```{r, results="asis"}
l("\u01B4")
```

Working on u01B5

```{r, results="asis"}
l("\u01B5")
```

Working on u01B6

```{r, results="asis"}
l("\u01B6")
```

Working on u01B7

```{r, results="asis"}
l("\u01B7")
```

Working on u01B8

```{r, results="asis"}
l("\u01B8")
```

Working on u01B9

```{r, results="asis"}
l("\u01B9")
```

Working on u01BA

```{r, results="asis"}
l("\u01BA")
```

Working on u01BB

```{r, results="asis"}
l("\u01BB")
```


Working on u01BC

```{r, results='asis'}
l('\u01BC')
```

Working on u01BD

```{r, results='asis'}
l('\u01BD')
```

Working on u01BE

```{r, results='asis'}
l('\u01BE')
```

Working on u01BF

```{r, results='asis'}
l('\u01BF')
```

Working on u01C0

```{r, results='asis'}
l('\u01C0')
```

Working on u01C1

```{r, results='asis'}
l('\u01C1')
```

Working on u01C2

```{r, results='asis'}
l('\u01C2')
```

Working on u01C3

```{r, results='asis'}
l('\u01C3')
```

Working on u01C4

```{r, results='asis'}
l('\u01C4')
```

Working on u01C5

```{r, results='asis'}
l('\u01C5')
```

Working on u01C6

```{r, results='asis'}
l('\u01C6')
```

Working on u01C7

```{r, results='asis'}
l('\u01C7')
```

Working on u01C8

```{r, results='asis'}
l('\u01C8')
```

Working on u01C9

```{r, results='asis'}
l('\u01C9')
```

Working on u01CA

```{r, results='asis'}
l('\u01CA')
```

Working on u01CB

```{r, results='asis'}
l('\u01CB')
```

Working on u01CC

```{r, results='asis'}
l('\u01CC')
```

Working on u01CD

```{r, results='asis'}
l('\u01CD')
```

Working on u01CE

```{r, results='asis'}
l('\u01CE')
```

Working on u01CF

```{r, results='asis'}
l('\u01CF')
```

Working on u01D0

```{r, results='asis'}
l('\u01D0')
```

Working on u01D1

```{r, results='asis'}
l('\u01D1')
```

Working on u01D2

```{r, results='asis'}
l('\u01D2')
```

Working on u01D3

```{r, results='asis'}
l('\u01D3')
```

Working on u01D4

```{r, results='asis'}
l('\u01D4')
```

Working on u01D5

```{r, results='asis'}
l('\u01D5')
```

Working on u01D6

```{r, results='asis'}
l('\u01D6')
```

Working on u01D7

```{r, results='asis'}
l('\u01D7')
```

Working on u01D8

```{r, results='asis'}
l('\u01D8')
```

Working on u01D9

```{r, results='asis'}
l('\u01D9')
```

Working on u01DA

```{r, results='asis'}
l('\u01DA')
```

Working on u01DB

```{r, results='asis'}
l('\u01DB')
```

Working on u01DC

```{r, results='asis'}
l('\u01DC')
```

Working on u01DD

```{r, results='asis'}
l('\u01DD')
```

Working on u01DE

```{r, results='asis'}
l('\u01DE')
```

Working on u01DF

```{r, results='asis'}
l('\u01DF')
```

Working on u01F0

```{r, results='asis'}
l('\u01F0')
```

Working on u01F1

```{r, results="asis"}
l("\u01F1")
```

Working on u01F2

```{r, results="asis"}
l("\u01F2")
```

Working on u01F3

```{r, results="asis"}
l("\u01F3")
```

Working on u01F4

```{r, results="asis"}
l("\u01F4")
```

Working on u01F5

```{r, results="asis"}
l("\u01F5")
```

Working on u01F6

```{r, results='asis'}
l('\u01F6')
```

Working on u01F7

```{r, results='asis'}
l('\u01F7')
```

Working on u01F8

```{r, results='asis'}
l('\u01F8')
```

Working on u01F9

```{r, results='asis'}
l('\u01F9')
```

Working on u01FA

```{r, results='asis'}
l('\u01FA')
```

Working on u01FB

```{r, results='asis'}
l('\u01FB')
```

Working on u01FC

```{r, results='asis'}
l('\u01FC')
```

Working on u01FD

```{r, results='asis'}
l('\u01FD')
```

Working on u01FE

```{r, results='asis'}
l('\u01FE')
```

Working on u01FF

```{r, results='asis'}
l('\u01FF')
```
