---
title: "LaTeX Raw"
author: "Shawn Garbett"
date: "July 13, 2018"
output:
  pdf_document:
    keep_tex: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tangram)
library(stringi)
```

```{r}
p <- function(...) { cat(paste0(...)); invisible(NULL) }
l <- function(...) { cat(tangram:::latexify(...)); invisible(NULL) }
```

## R Markdown
```{r, results='asis'}
p("\\textbf{This is a test of LaTeX}")
```

Working on u007D 

```{r, results="asis"}
l("{")
```

Working on u000a 

```{r, results="asis"}
l("}")
```

Working on vspace (look between a b)

```{r, results="asis"}
p("a", latexify("\u000a\u000a"), "b", sep='')
```

```{r, results="asis"}
p("a", latexify("\u000d\u000a\u000d\u000a"), "b")
```

Working on u0023

```{r, results="asis"}
l("\\#")
```

Working on u0024 

```{r, results="asis"}
l("\\$")
```

Working on u0025 

```{r, results="asis"}
l("%")
```

Working on u0026 

```{r, results="asis"}
l("&")
```

Working on u0027 

```{r, results="asis"}
l("'")
```

Working on u002A 

```{r, results="asis"}
l("\\*")
```

Working on u003C

```{r, results="asis"}
l("<")
```

Working on u003E

```{r, results="asis"}
l(">")
```

Working on u005E

```{r, results="asis"}
l("^")
```

Working on u005F

```{r, results="asis"}
l("_")
```

Working on u0060

```{r, results="asis"}
l("`")
```

Working on u007c

```{r, results="asis"}
l("|")
```

Working on u007e

```{r, results="asis"}
l("~")
```

Working on u00A1 

```{r, results="asis"}
l("\u00A1")
```

Working on u00A2 

```{r, results="asis"}
l("\u00A2")
```

Working on u00A3 

```{r, results="asis"}
l("\u00A3")
```

Working on u00A4 

```{r, results="asis"}
l("\u00A4")
```

Working on u00A5 

```{r, results="asis"}
l("\u00A5")
```

Working on u00A6 

```{r, results="asis"}
l("\u00A6")
```

Working on u00A7 

```{r, results="asis"}
l("\u00A7")
```

Working on u00A8 

```{r, results="asis"}
l("\u00A8")
```

Working on u00A9 

```{r, results="asis"}
l("\u00A9")
```

Working on u00AA 

```{r, results="asis"}
l("\u00AA")
```

Working on u00AB 

```{r, results="asis"}
l("\u00AB")
```

Working on u00AC 

```{r, results="asis"}
l("\u00AC")
```

Working on u00AD 

```{r, results="asis"}
l("\u00AD")
```

Working on u00AE 

```{r, results="asis"}
l("\u00AE")
```

Working on u00AF 

```{r, results="asis"}
l("\u00AF")
```


Working on u00B0

```{r, results="asis"}
l("\u00B0")
```

Working on u00B1

```{r, results="asis"}
l("\u00B1")
```

Working on u00B2

```{r, results="asis"}
l("\u00B2")
```

Working on u00B3

```{r, results="asis"}
l("\u00B3")
```

Working on u00B4

```{r, results="asis"}
l("\u00B4")
```

Working on u00B5

```{r, results="asis"}
l("\u00B5")
```

Working on u00B6

```{r, results="asis"}
l("\u00B6")
```

Working on u00B7

```{r, results="asis"}
l("\u00B7")
```

Working on u00B8

```{r, results="asis"}
l("\u00B8")
```

Working on u00B9

```{r, results="asis"}
l("\u00B9")
```

Working on u00BA

```{r, results="asis"}
l("\u00BA")
```

Working on u00BB

```{r, results="asis"}
l("\u00BB")
```

Working on u00BC

```{r, results="asis"}
l("\u00BC")
```

Working on u00BD

```{r, results="asis"}
l("\u00BD")
```

Working on u00BE

```{r, results="asis"}
l("\u00BE")
```

Working on u00BF

```{r, results="asis"}
l("\u00BF")
```

Working on u00C0

```{r, results="asis"}
l("\u00C0")
```

Working on u00C1

```{r, results="asis"}
l("\u00C1")
```

Working on u00C2

```{r, results="asis"}
l("\u00C2")
```

Working on u00C3

```{r, results="asis"}
l("\u00C3")
```

Working on u00C4

```{r, results="asis"}
l("\u00C4")
```

Working on u00C5

```{r, results="asis"}
l("\u00C5")
```

Working on u00C6

```{r, results="asis"}
l("\u00C6")
```

Working on u00C7

```{r, results="asis"}
l("\u00C7")
```

Working on u00C8

```{r, results="asis"}
l("\u00C8")
```

Working on u00C9

```{r, results="asis"}
l("\u00C9")
```

Working on u00CA

```{r, results="asis"}
l("\u00CA")
```

Working on u00CB

```{r, results="asis"}
l("\u00CB")
```

Working on u00CC

```{r, results="asis"}
l("\u00CC")
```

Working on u00CD

```{r, results="asis"}
l("\u00CD")
```

Working on u00CE

```{r, results="asis"}
l("\u00CE")
```

Working on u00CF

```{r, results="asis"}
l("\u00CF")
```

Working on u00D0

```{r, results="asis"}
l("\u00D0")
```

Working on u00D1

```{r, results="asis"}
l("\u00D1")
```

Working on u00D2

```{r, results="asis"}
l("\u00D2")
```

Working on u00D3

```{r, results="asis"}
l("\u00D3")
```

Working on u00D4

```{r, results="asis"}
l("\u00D4")
```

Working on u00D5

```{r, results="asis"}
l("\u00D5")
```

Working on u00D6

```{r, results="asis"}
l("\u00D6")
```

Working on u00D7

```{r, results="asis"}
l("\u00D7")
```

Working on u00D8

```{r, results="asis"}
l("\u00D8")
```

Working on u00D9

```{r, results="asis"}
l("\u00D9")
```

Working on u00DA

```{r, results="asis"}
l("\u00DA")
```

Working on u00DB

```{r, results="asis"}
l("\u00DB")
```

Working on u00DC

```{r, results="asis"}
l("\u00DC")
```

Working on u00DD

```{r, results="asis"}
l("\u00DD")
```

Working on u00DE

```{r, results="asis"}
l("\u00DE")
```

Working on u00DF

```{r, results="asis"}
l("\u00DF")
```

Working on u00E0

```{r, results="asis"}
l("\u00E0")
```

Working on u00E1

```{r, results="asis"}
l("\u00E1")
```

Working on u00E2

```{r, results="asis"}
l("\u00E2")
```

Working on u00E3

```{r, results="asis"}
l("\u00E3")
```

Working on u00E4

```{r, results="asis"}
l("\u00E4")
```

Working on u00E5

```{r, results="asis"}
l("\u00E5")
```

Working on u00E6

```{r, results="asis"}
l("\u00E6")
```

Working on u00E7

```{r, results="asis"}
l("\u00E7")
```

Working on u00E8

```{r, results="asis"}
l("\u00E8")
```

Working on u00E9

```{r, results="asis"}
l("\u00E9")
```

Working on u00EA

```{r, results="asis"}
l("\u00EA")
```

Working on u00EB

```{r, results="asis"}
l("\u00EB")
```

Working on u00EC

```{r, results="asis"}
l("\u00EC")
```

Working on u00ED

```{r, results="asis"}
l("\u00ED")
```

Working on u00EE

```{r, results="asis"}
l("\u00EE")
```

Working on u00EF

```{r, results="asis"}
l("\u00EF")
```

Working on u00F0

```{r, results="asis"}
l("\u00F0")
```

Working on u00F1

```{r, results="asis"}
l("\u00F1")
```

Working on u00F2

```{r, results="asis"}
l("\u00F2")
```

Working on u00F3

```{r, results="asis"}
l("\u00F3")
```

Working on u00F4

```{r, results="asis"}
l("\u00F4")
```

Working on u00F5

```{r, results="asis"}
l("\u00F5")
```

Working on u00F6

```{r, results="asis"}
l("\u00F6")
```

Working on u00F7

```{r, results="asis"}
l("\u00F7")
```

Working on u00F8

```{r, results="asis"}
l("\u00F8")
```

Working on u00F9

```{r, results="asis"}
l("\u00F9")
```

Working on u00FA

```{r, results="asis"}
l("\u00FA")
```

Working on u00FB

```{r, results="asis"}
l("\u00FB")
```

Working on u00FC

```{r, results="asis"}
l("\u00FC")
```

Working on u00FD

```{r, results="asis"}
l("\u00FD")
```

Working on u00FE

```{r, results="asis"}
l("\u00FE")
```

Working on u00FF

```{r, results="asis"}
l("\u00FF")
```

And that completes page 00
