---
title: "LaTeX Raw Page 02"
author: "Shawn Garbett"
date: "July 13, 2018"
output:
  pdf_document:
    keep_tex: yes
header-includes:
- \usepackage{textgreek}
- \usepackage{amsmath,mathtools}
- \usepackage{textcomp}
- \usepackage{tipx}
- \usepackage{ipa}
- \usepackage{slashed}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tangram)
library(stringi)
```

```{r}
p <- function(...) { cat(paste0(...)); invisible(NULL) }
l <- function(...) { cat(tangram:::latexify(...)); invisible(NULL) }
```

## R Markdown
```{r, results='asis'}
p("\\textbf{This is a test of LaTeX}")
```

Working on u0200

```{r, results="asis"}
l("\u0200")
```

Working on u0201

```{r, results="asis"}
l("\u0201")
```

Working on u0202

```{r, results="asis"}
l("\u0202")
```

Working on u0203

```{r, results="asis"}
l("\u0203")
```

Working on u0204

```{r, results="asis"}
l("\u0204")
```

Working on u0205

```{r, results="asis"}
l("\u0205")
```

Working on u0206

```{r, results="asis"}
l("\u0206")
```

Working on u0207

```{r, results="asis"}
l("\u0207")
```

Working on u0208

```{r, results="asis"}
l("\u0208")
```

Working on u0209

```{r, results="asis"}
l("\u0209")
```

Working on u0210

```{r, results='asis'}
l('\u0210')
```

Working on u0211

```{r, results='asis'}
l('\u0211')
```

Working on u0212

```{r, results='asis'}
l('\u0212')
```

Working on u0213

```{r, results='asis'}
l('\u0213')
```

Working on u0214

```{r, results='asis'}
l('\u0214')
```

Working on u0215

```{r, results='asis'}
l('\u0215')
```

Working on u0216

```{r, results='asis'}
l('\u0216')
```

Working on u0217

```{r, results='asis'}
l('\u0217')
```

Working on u0218

```{r, results='asis'}
l('\u0218')
```

Working on u0219

```{r, results='asis'}
l('\u0219')
```

Working on u021A

```{r, results='asis'}
l('\u021A')
```

Working on u021B

```{r, results='asis'}
l('\u021B')
```

Working on u021C

```{r, results='asis'}
l('\u021C')
```

Working on u021D

```{r, results='asis'}
l('\u021D')
```

Working on u021E

```{r, results='asis'}
l('\u021E')
```

Working on u021F

```{r, results='asis'}
l('\u021F')
```

Working on u0220

<!-- ```{r, results='asis'} -->
<!-- l('\u0220') -->
<!-- ``` -->

*UNSUPPORTED*

Working on u0221

```{r, results='asis'}
l('\u0221')
```

Working on u0222

<!-- ```{r, results='asis'} -->
<!-- l('\u0222') -->
<!-- ``` -->

*UNSUPPORTED*

Working on u0223

<!-- ```{r, results='asis'} -->
<!-- l('\u0223') -->
<!-- ``` -->

*UNSUPPORTED*

Working on u0224

```{r, results='asis'}
l('\u0224')
```

Working on u0225

```{r, results='asis'}
l('\u0225')
```

Working on u0226

```{r, results='asis'}
l('\u0226')
```

Working on u0227

```{r, results='asis'}
l('\u0227')
```

Working on u0228

```{r, results='asis'}
l('\u0228')
```

Working on u0229

```{r, results='asis'}
l('\u0229')
```

Working on u022A

```{r, results='asis'}
l('\u022A')
```

Working on u022B

```{r, results='asis'}
l('\u022B')
```

Working on u022C

```{r, results='asis'}
l('\u022C')
```

Working on u022D

```{r, results='asis'}
l('\u022D')
```

Working on u022E

```{r, results='asis'}
l('\u022E')
```

Working on u022F

```{r, results='asis'}
l('\u022F')
```

Working on u0230

```{r, results='asis'}
l('\u0230')
```

Working on u0231

```{r, results='asis'}
l('\u0231')
```

Working on u0232

```{r, results='asis'}
l('\u0232')
```

Working on u0233

```{r, results='asis'}
l('\u0233')
```

Working on u0234

<!-- ```{r, results='asis'} -->
<!-- l('\u0234') -->
<!-- ``` -->

*UNSUPPORTED*

Working on u0235

```{r, results='asis'}
l('\u0235')
```

Working on u0236

```{r, results='asis'}
l('\u0236')
```

Working on u0237

```{r, results='asis'}
l('\u0237')
```

Working on u0238

```{r, results='asis'}
l('\u0238')
```

Working on u0239

```{r, results='asis'}
l('\u0239')
```

Working on u023A

```{r, results='asis'}
l('\u023A')
```

Working on u023B

```{r, results='asis'}
l('\u023B')
```

Working on u023C

```{r, results='asis'}
l('\u023C')
```

Working on u023D

```{r, results='asis'}
l('\u023D')
```

Working on u023E

```{r, results='asis'}
l('\u023E')
```

Working on u023F

<!-- ```{r, results='asis'} -->
<!-- l('\u023F') -->
<!-- ``` -->

*UNSUPPORTED*

Working on u0240

```{r, results='asis'}
l('\u0240')
```

Working on u0241

```{r, results='asis'}
l('\u0241')
```

Working on u0242

```{r, results='asis'}
l('\u0242')
```

Working on u0243

```{r, results='asis'}
l('\u0243')
```

Working on u0244

```{r, results='asis'}
l('\u0244')
```

Working on u0245

```{r, results='asis'}
l('\u0245')
```

Working on u0246

```{r, results='asis'}
l('\u0246')
```

Working on u0247

```{r, results='asis'}
l('\u0247')
```

Working on u0248

```{r, results='asis'}
l('\u0248')
```

Working on u0249

```{r, results='asis'}
l('\u0249')
```

Working on u024A

<!-- ```{r, results='asis'} -->
<!-- l('\u024A') -->
<!-- ``` -->

*UNSUPPORTED*

Working on u024B

<!-- ```{r, results='asis'} -->
<!-- l('\u024B') -->
<!-- ``` -->

*UNSUPPORTED*

Working on u024C

```{r, results='asis'}
l('\u024C')
```

Working on u024D

```{r, results='asis'}
l('\u024D')
```

Working on u024E

```{r, results='asis'}
l('\u024E')
```

Working on u024F

```{r, results='asis'}
l('\u024F')
```

Working on u0250

```{r, results="asis"}
l("\u0250")
```

Working on u0251

```{r, results="asis"}
l("\u0251")
```

Working on u0252

```{r, results="asis"}
l("\u0252")
```

Working on u0253

```{r, results="asis"}
l("\u0253")
```

Working on u0254

```{r, results="asis"}
l("\u0254")
```

Working on u0255

```{r, results="asis"}
l("\u0255")
```

Working on u0256

```{r, results="asis"}
l("\u0256")
```

Working on u0257

```{r, results="asis"}
l("\u0257")
```

Working on u0258

```{r, results="asis"}
l("\u0258")
```

Working on u0259

```{r, results="asis"}
l("\u0259")
```

Working on u025A

```{r, results='asis'}
l('\u025A')
```

Working on u025B

```{r, results='asis'}
l('\u025B')
```

Working on u025C

```{r, results='asis'}
l('\u025C')
```

Working on u025D

```{r, results='asis'}
l('\u025D')
```

Working on u025E

```{r, results='asis'}
l('\u025E')
```

Working on u025F

```{r, results='asis'}
l('\u025F')
```

Working on u0260

```{r, results='asis'}
l('\u0260')
```

Working on u0261

```{r, results='asis'}
l('\u0261')
```

Working on u0262

```{r, results='asis'}
l('\u0262')
```


Working on u0263

```{r, results="asis"}
l("\u0263")
```

Working on u0264

```{r, results="asis"}
l("\u0264")
```

Working on u0265

```{r, results="asis"}
l("\u0265")
```

Working on u0266

```{r, results='asis'}
l('\u0266')
```

Working on u0267

```{r, results='asis'}
l('\u0267')
```

Working on u0268

```{r, results='asis'}
l('\u0268')
```

Working on u0269

```{r, results='asis'}
l('\u0269')
```

Working on u026A

```{r, results='asis'}
l('\u026A')
```

Working on u026B

```{r, results='asis'}
l('\u026B')
```

Working on u026C

```{r, results="asis"}
l("\u026C")
```

Working on u026D

```{r, results="asis"}
l("\u026D")
```

Working on u026F

```{r, results="asis"}
l("\u026F")
```

Working on u0270

```{r, results="asis"}
l("\u0270")
```

Working on u0271

```{r, results="asis"}
l("\u0271")
```

Working on u0272

```{r, results="asis"}
l("\u0272")
```

Working on u0273

```{r, results="asis"}
l("\u0273")
```

Working on u0274

```{r, results="asis"}
l("\u0274")
```

Working on u0275

```{r, results="asis"}
l("\u0275")
```

Working on u0276

```{r, results="asis"}
l("\u0276")
```


Working on u0277

```{r, results="asis"}
l("\u0277")
```

Working on u0278

```{r, results="asis"}
l("\u0278")
```

Working on u0279

```{r, results="asis"}
l("\u0279")
```

Working on u027A

```{r, results="asis"}
l("\u027A")
```

Working on u027B

```{r, results="asis"}
l("\u027B")
```

Working on u027C

```{r, results="asis"}
l("\u027C")
```

Working on u027D

```{r, results="asis"}
l("\u027D")
```

Working on u027E

```{r, results="asis"}
l("\u027E")
```

Working on u027F

```{r, results="asis"}
l("\u027F")
```

Working on u0280

```{r, results='asis'}
l('\u0280')
```

Working on u0281

```{r, results='asis'}
l('\u0281')
```

Working on u0282

```{r, results='asis'}
l('\u0282')
```

Working on u0283

```{r, results='asis'}
l('\u0283')
```

Working on u0284

```{r, results='asis'}
l('\u0284')
```

Working on u0285

```{r, results='asis'}
l('\u0285')
```

Working on u0286

```{r, results='asis'}
l('\u0286')
```

Working on u0287

```{r, results='asis'}
l('\u0287')
```

Working on u0288

```{r, results='asis'}
l('\u0288')
```

Working on u0289

```{r, results='asis'}
l('\u0289')
```

Working on u028A

```{r, results='asis'}
l('\u028A')
```

Working on u028B

```{r, results='asis'}
l('\u028B')
```

Working on u028C

```{r, results='asis'}
l('\u028C')
```

Working on u028D

```{r, results='asis'}
l('\u028D')
```

Working on u028E

```{r, results='asis'}
l('\u028E')
```

Working on u028F

```{r, results='asis'}
l('\u028F')
```

Working on u0290

```{r, results="asis"}
l("\u0290")
```

Working on u0291

```{r, results="asis"}
l("\u0291")
```

Working on u0292

```{r, results="asis"}
l("\u0292")
```

Working on u0293

```{r, results="asis"}
l("\u0293")
```

Working on u0294

```{r, results="asis"}
l("\u0294")
```

Working on u0295

```{r, results="asis"}
l("\u0295")
```

Working on u0296

```{r, results="asis"}
l("\u0296")
```

Working on u0297

```{r, results="asis"}
l("\u0297")
```

Working on u0298

```{r, results="asis"}
l("\u0298")
```

Working on u0299

```{r, results="asis"}
l("\u0299")
```

Working on u029A

```{r, results="asis"}
l("\u029a")
```

Working on u029B

```{r, results="asis"}
l("\u029b")
```

Working on u029C

```{r, results="asis"}
l("\u029c")
```

Working on u029D

```{r, results="asis"}
l("\u029d")
```

Working on u029E

```{r, results="asis"}
l("\u029E")
```

Working on u029F

```{r, results="asis"}
l("\u029F")
```

Working on u02A0

```{r, results='asis'}
l('\u02A0')
```

Working on u02A1

```{r, results='asis'}
l('\u02A1')
```

Working on u02A2

```{r, results='asis'}
l('\u02A2')
```

Working on u02A3

```{r, results='asis'}
l('\u02A3')
```

Working on u02A4

```{r, results='asis'}
l('\u02A4')
```

Working on u02A5

```{r, results='asis'}
l('\u02A5')
```

Working on u02A6

```{r, results='asis'}
l('\u02A6')
```

Working on u02A7

```{r, results='asis'}
l('\u02A7')
```

Working on u02A8

```{r, results='asis'}
l('\u02A8')
```

Working on u02A9

```{r, results='asis'}
l('\u02A9')
```

Working on u02AA

```{r, results='asis'}
l('\u02AA')
```

Working on u02AB

```{r, results='asis'}
l('\u02AB')
```

Working on u02AC

<!-- ```{r, results='asis'} -->
<!-- l('\u02AC') -->
<!-- ``` -->

*UNSUPPORTED*

Working on u02AD

<!-- ```{r, results='asis'} -->
<!-- l('\u02AD') -->
<!-- ``` -->

*UNSUPPORTED*

Working on u02AE

```{r, results='asis'}
l('\u02AE')
```

Working on u02AF

```{r, results='asis'}
l('\u02AF')
```
