---
title: "LaTeX Raw Page 02"
author: "Shawn Garbett"
date: "July 13, 2018"
output:
  pdf_document:
    keep_tex: yes
header-includes:
- \usepackage{textgreek}
- \usepackage{amsmath,mathtools}
- \usepackage{textcomp}
- \usepackage{tipx}
- \usepackage{ipa}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tangram)
library(stringi)
```

```{r}
p <- function(...) { cat(paste0(...)); invisible(NULL) }
l <- function(...) { cat(tangram:::latexify(...)); invisible(NULL) }
```

## R Markdown
```{r, results='asis'}
p("\\textbf{This is a test of LaTeX}")
```

Working on u0200

```{r, results="asis"}
l("\u0200")
```

Working on u0201

```{r, results="asis"}
l("\u0201")
```

Working on u0202

```{r, results="asis"}
l("\u0202")
```

Working on u0203

```{r, results="asis"}
l("\u0203")
```

Working on u0204

```{r, results="asis"}
l("\u0204")
```

Working on u0205

```{r, results="asis"}
l("\u0205")
```

Working on u0206

```{r, results="asis"}
l("\u0206")
```

Working on u0207

```{r, results="asis"}
l("\u0207")
```

Working on u0208

```{r, results="asis"}
l("\u0208")
```

Working on u0209

```{r, results="asis"}
l("\u0209")
```

Working on u0210

```{r, results='asis'}
l('\u0210')
```

Working on u0211

```{r, results='asis'}
l('\u0211')
```

Working on u0212

```{r, results='asis'}
l('\u0212')
```

Working on u0213

```{r, results='asis'}
l('\u0213')
```

Working on u0214

```{r, results='asis'}
l('\u0214')
```

Working on u0215

```{r, results='asis'}
l('\u0215')
```

Working on u0216

```{r, results='asis'}
l('\u0216')
```

Working on u0217

```{r, results='asis'}
l('\u0217')
```

Working on u0218

```{r, results='asis'}
l('\u0218')
```

Working on u0219

```{r, results='asis'}
l('\u0219')
```

Working on u021A

```{r, results='asis'}
l('\u021A')
```

Working on u021B

```{r, results='asis'}
l('\u021B')
```

Working on u021C

```{r, results='asis'}
l('\u021C')
```

Working on u021D

```{r, results='asis'}
l('\u021D')
```

Working on u021E

```{r, results='asis'}
l('\u021E')
```

Working on u021F

```{r, results='asis'}
l('\u021F')
```

Working on u0250

```{r, results="asis"}
l("\u0250")
```

Working on u0252

```{r, results="asis"}
l("\u0252")
```

Working on u0254

```{r, results="asis"}
l("\u0254")
```

Working on u0256

```{r, results="asis"}
l("\u0256")
```

Working on u0258

```{r, results="asis"}
l("\u0258")
```

Working on u0259

```{r, results="asis"}
l("\u0259")
```

Working on u025B

```{r, results="asis"}
l("\u025B")
```


Working on u0263

```{r, results="asis"}
l("\u0263")
```

Working on u0264

```{r, results="asis"}
l("\u0264")
```

Working on u0265

```{r, results="asis"}
l("\u0265")
```

Working on u026C

```{r, results="asis"}
l("\u026C")
```

Working on u026D

```{r, results="asis"}
l("\u026D")
```

Working on u026F

```{r, results="asis"}
l("\u026F")
```


Working on u0270

```{r, results="asis"}
l("\u0270")
```

Working on u0271

```{r, results="asis"}
l("\u0271")
```

Working on u0272

```{r, results="asis"}
l("\u0272")
```

Working on u0273

```{r, results="asis"}
l("\u0273")
```

Working on u0277

```{r, results="asis"}
l("\u0277")
```

Working on u0278

```{r, results="asis"}
l("\u0278")
```

Working on u0279

```{r, results="asis"}
l("\u0279")
```

Working on u027A

```{r, results="asis"}
l("\u027A")
```

Working on u027B

```{r, results="asis"}
l("\u027B")
```

Working on u027C

```{r, results="asis"}
l("\u027C")
```

Working on u027D

```{r, results="asis"}
l("\u027D")
```

Working on u027E

```{r, results="asis"}
l("\u027E")
```

Working on u027F

```{r, results="asis"}
l("\u027F")
```


Working on u0282

```{r, results="asis"}
l("\u0282")
```

Working on u0283

```{r, results="asis"}
l("\u0283")
```

Working on u0287

```{r, results="asis"}
l("\u0287")
```

Working on u0288

```{r, results="asis"}
l("\u0288")
```

Working on u028A

```{r, results="asis"}
l("\u028A")
```

Working on u028B

```{r, results="asis"}
l("\u028B")
```

Working on u028C

```{r, results="asis"}
l("\u028C")
```

Working on u028D

```{r, results="asis"}
l("\u028D")
```

Working on u028E

```{r, results="asis"}
l("\u028E")
```

Working on u0290

```{r, results="asis"}
l("\u0290")
```

Working on u0291

```{r, results="asis"}
l("\u0291")
```

Working on u0292

```{r, results="asis"}
l("\u0292")
```

Working on u0293

```{r, results="asis"}
l("\u0293")
```

Working on u0294

```{r, results="asis"}
l("\u0294")
```

Working on u0295

```{r, results="asis"}
l("\u0295")
```

Working on u0296

```{r, results="asis"}
l("\u0296")
```

Working on u0297

```{r, results="asis"}
l("\u0297")
```

Working on u0298

```{r, results="asis"}
l("\u0298")
```

Working on u0299

```{r, results="asis"}
l("\u0299")
```

Working on u029a

```{r, results="asis"}
l("\u029a")
```

Working on u029b

```{r, results="asis"}
l("\u029b")
```

Working on u029c

```{r, results="asis"}
l("\u029c")
```

Working on u029d

```{r, results="asis"}
l("\u029d")
```


Working on u029E

```{r, results="asis"}
l("\u029E")
```
